---
title: "Experiment A Data Read-in"
author: "Rachel"
date: /today
geometry: margin = 2cm
header-includes:
  - /usepackage{booktabs}
  - /usepackage{siunitx}
  - /usepackage{tabto}
  - /usepackage{soul}
  - /usepackage{xcolor}
  - /usepackage{placeins}
  - /usepackage{lscape}
  - /usepackage{animate}
  - /newcommand{/blandscape}{/begin{landscape}}
  - /newcommand{/elandscape}{/end{landscape}}
  - /makeatletter/renewcommand{/fps@table}{!ht}/makeatother
  - /setstcolor{red}
  - /usepackage{sectsty}
  - /sectionfont{/color{blue}} 
  - /subsectionfont{/color{blue}}
  - /subsubsectionfont{/color{darkgray}}

output:
  pdf_document: 
    fig_caption: yes
    fig_width: 7
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
    toc: yes
    toc_depth: 4
  fontsize: 10pt
editor_options: 
  chunk_output_type: inline
---   
***
# Housekeeping   
The purpose of this file is to create the lists for Experiment 1.  
_Goal:_ To create csv files that contain the .wav filenames to be called for every possible block in Experiment A.  
*Color file here: http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf*  
*crtl + I for reformat*   

## Knitting    
```{r Knitting, include=F}

library(knitr)

opts_chunk$set(
  dev = 'pdf',
  comment = "", 
  echo = FALSE, 
  warning = TRUE, 
  message = TRUE,
  cache = FALSE, 
  size = "small",
  tidy.opts = list(width.cutoff = 200),
  fig.width = 8, 
  fig.height = 4.5, 
  fig.align = "center")

def.chunk.hook  <- knitr::knit_hooks$get("chunk")

knitr::knit_hooks$set(
  chunk = function(x, options) {
    x <- def.chunk.hook(x, options)
    ifelse(
      options$size != "normalsize", 
      paste0(
        "/n //", 
        options$size,
        "/n/n", 
        x, 
        "/n/n //normalsize"), 
      x)
  })

color_block = function(color) {
  function(x, options)        sprintf('//color{%s}//begin{verbatim}%s//end{verbatim}//color{black}', color, x)
}
knitr::knit_hooks$set(error = color_block('red'))
knitr::knit_hooks$set(warning = color_block('orange'))
```

## Libraries   
```{r Library, include=F}
library(readr)
library(dplyr)
library(tidyverse)
library(magrittr)
library(broom)          # for extraction of coefficients
library(gganimate)      # to animate plots
library(RColorBrewer)   # to select brewer colors
library(kableExtra) 
library(lme4)
library(lmerTest)
library(ggpubr)
library(data.table)
library(jsonlite)
library(purrr)
```

```{r, Format, include=F}
options(width = 110)
theme_set(theme_bw())
```

____

# Remove Extra participants  
## I work but am not needed  
```{r}
data <- list.files(
  path = "C:/Users/Rachel/Documents/SI.SP/data", 
  full.names = T,
  pattern = "^Attention")

for (f in data) {
 Remove <- read.csv(f)
    Removed.data <- subset(Remove,
      E$workerid != "531" &
      E$workerid != "533" &
      E$workerid != "509" &
      E$workerid != "534" &
      E$workerid != "523" &
      E$workerid != "517" &
      E$workerid != "524" &
      E$workerid != "521" &
      E$workerid != "508"
    )
    write.csv(Removed.data, f)
}
```

# File Rename   
```{r file.rename}
Files <- list.files(path = "C:/Users/Rachel/Documents/SI.SP/data/Pilot_03.06_11/")

for (f in Files) {
  
  old.files <- paste0(
    "C:/Users/Rachel/Documents/SI.SP/data/Experiment.A_03.15_9/",
    f) 
  
  f.new = gsub("Attention_", "V2_Attention_", f)
  
  new.files <- paste0("C:/Users/Rachel/Documents/SI.SP/data/", f.new)
  
  file.rename(old.files, new.files)
}
```

_______

# Combine CSVs across experiments
```{r Concat Experiments}

Exp.A <- list.files(
  path = "C:/Users/Rachel/Documents/SI.SP/data", 
  full.names = T,
  pattern = "^Attention")
  
Pilot <- list.files(
  path = "C:/Users/Rachel/Documents/SI.SP/data", 
  pattern = "^Pilot_Attention")

V2 <- list.files(
  path = "C:/Users/Rachel/Documents/SI.SP/data", 
  pattern = "^V2_Attention")

for (a in Exp.A){
  A <- read.csv(a)
  b <- gsub("Attention", "Pilot_Attention", a)  
  B <- read.csv(b)
  D <- rbind(A,B)
  c <- gsub("Attention", "V2_Attention", a)
  C <- read.csv(C)
  
  write.csv(rbind(C, D), a)
}

# lowercase: file name
# uppercase: CSV file

# A/a: Exp.A (53 participants)
# B/b: Pilot (11 participants)
# C/c: Exp.B (9 participants)
```  

## Remove other file versions  
```{r}
Path <- "C:/Users/Rachel/Documents/SI.SP/data/"

X <- list.files(
  path = "C:/Users/Rachel/Documents/SI.SP/data", 
  pattern = "_Attention")

Remove.Files <- paste0(Path, X)

file.remove(Remove.Files)

# Also do not need data from these CSV files
file.remove(
  c(
  "C:/Users/Rachel/Documents/SI.SP/data/Attention_PR-workerids.csv", 
  "C:/Users/Rachel/Documents/SI.SP/data/Attention_PR-platform.csv")
 # Note useful but keep for now "C:/Users/Rachel/Documents/SI.SP/data/Attention_PR-AttendedTalkerEar.csv",
 # Note useful but keep for now "C:/Users/Rachel/Documents/SI.SP/data/Attention_PR-AttendedTalkerMaterial.csv"
)
```

## Remove unnecessary columns from individual files
```{r}
Exp.A <- list.files(
  path = "C:/Users/Rachel/Documents/SI.SP/data", 
  full.names = T,
  pattern = "^Attention")

for (a in Exp.A){
  read.csv(a) %>%
  select(-c("X","error","proliferate.condition"))
}
```

# Join data by workerid
```{r Combine data}
file.list <- list.files(
  "C:/Users/Rachel/Documents/SI.SP/data", 
  full.names = TRUE, 
  pattern = ".csv")

# empty data frame for loop to store
## Large enough to have a place for all workerids
result <- data.frame(workerid = 405:600)

for (f in file.list) {
  Data <- read.csv(f) 
  Data2 <- Data [,-1]
  result <- left_join(result, Data2, by = "workerid") %>%
    filter(!is.na(AttendedTalkerEar)) ## removes unused workerids
  write.csv(
    result, 
    "C:/Users/Rachel/Documents/SI.SP/data/data.csv", 
    row.names = FALSE)
}
```


