---
title: "Experiment A List Design"
author: "Rachel"
date: /today
geometry: margin = 2cm
header-includes:
  - /usepackage{booktabs}
  - /usepackage{siunitx}
  - /usepackage{tabto}
  - /usepackage{soul}
  - /usepackage{xcolor}
  - /usepackage{placeins}
  - /usepackage{lscape}
  - /usepackage{animate}
  - /newcommand{/blandscape}{/begin{landscape}}
  - /newcommand{/elandscape}{/end{landscape}}
  - /makeatletter/renewcommand{/fps@table}{!ht}/makeatother
  - /setstcolor{red}
  - /usepackage{sectsty}
  - /sectionfont{/color{blue}} 
  - /subsectionfont{/color{blue}}
  - /subsubsectionfont{/color{darkgray}}
output:
  pdf_document: 
    fig_caption: yes
    fig_width: 7
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
    toc: yes
    toc_depth: 4
  fontsize: 10pt
editor_options: 
  chunk_output_type: inline
---   
***
# Housekeeping   
The purpose of this file is to analyze the data collected in Experiment 1.  
_Goal:_ To determine how participant's adapted their perception to the Attended and Unattended Talkers.  
*Color file here: http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf*  
*crtl + I for reformat*   

## Knitting    
```{r Knitting, include=F}

library(knitr)

opts_chunk$set(
  dev = 'pdf',
  comment = "", 
  echo = FALSE, 
  warning = TRUE, 
  message = TRUE,
  cache = FALSE, 
  size = "small",
  tidy.opts = list(width.cutoff = 200),
  fig.width = 8, 
  fig.height = 4.5, 
  fig.align = "center")

def.chunk.hook  <- knitr::knit_hooks$get("chunk")

knitr::knit_hooks$set(
  chunk = function(x, options) {
    x <- def.chunk.hook(x, options)
    ifelse(
      options$size != "normalsize", 
      paste0(
        "/n //", 
        options$size,
        "/n/n", 
        x, 
        "/n/n //normalsize"), 
      x)
  })

color_block = function(color) {
  function(x, options)        sprintf('//color{%s}//begin{verbatim}%s//end{verbatim}//color{black}', color, x)
}
knitr::knit_hooks$set(error = color_block('red'))
knitr::knit_hooks$set(warning = color_block('orange'))
```

## Libraries   
```{r Library, include=F}
library(htmltools)
library(Hmisc)
library(readr)
library(dplyr)
library(tidyverse)
library(magrittr)
library(broom)          # for extraction of coefficients
library(gganimate)      # to animate plots
library(RColorBrewer)   # to select brewer colors
library(kableExtra) 
library(lme4)
library(lmerTest)
library(ggpubr)
library(data.table)
library(jsonlite)
library(purrr)
```

```{r, Format, include=F}
options(width = 110)
theme_set(theme_bw())
```
_____
```{r}
## Altered the sortVars function to accommodate my data 
sortVars <- function(.data) {
  .data %>%
    relocate(
      ParticipantID,
      Phase,
      Block,
      Trial,
      starts_with("Item."), 
      Response,
      Response.Correct,
      Attended.Talker_Item,
      Attended.Talker_Gender,
      Attended.Talker_Ear,
      Attended.Talker_Sound,
      starts_with("Attended.Talker"),
      Unattended.Talker_Item,
      Unattended.Talker_Gender,
      Unattended.Talker_Ear,
      Unattended.Talker_Sound,
      starts_with("Unattended.Talker"),
      Filename,
      Correct_Attended.Talker,
      ExposureOrder,
      TestOrder,
      TrialOrder,
      starts_with("Condition_"),
      starts_with("resp"),
      starts_with("Response"),
      starts_with("speaker_"),
      Assignment.Comment,
      starts_with("Participant."), 
      starts_with("audio_"),
      starts_with("Duration"),
      starts_with("Time"),
      starts_with("Assignment.Submit"),
      userDateTimeAtSubmit,
      userDateTimeAtInitialization,
      userAgent,
      word_recall,
      participant_id,
      everything())
}
```

# Reformat Raw Data  
```{r data}
experiment = "experiment.a"
  read_csv(
    "C:/Users/Rachel/Documents/SI.SP/data/exp.1_data_raw.csv",
    show_col_types = FALSE) %>%

formatData(experiment) %>%
sortVars() %>%
  #view()
  write.csv(., "C:/Users/Rachel/Documents/SI.SP/data/exp.1_data.csv")
```
_____

# Data from Prolific   
```{r data}
data <- read_csv("C:/Users/Rachel/Documents/SI.SP/data/exp.1_data.csv",
    show_col_types = FALSE)
```

## Data Check  
```{r Checks}
# All should return 0!

# Have any participants completed the experiment more than once?  
data %>%
  group_by(ParticipantID, userDateTimeAtInitialization) %>%
  summarise() %>%
  group_by(ParticipantID) %>%
  tally() %>% 
  filter(n != 1)

# Are there the right number of Blocks?  
data %>%
  group_by(ParticipantID, Block) %>%
  summarise() %>%   
  tally() %>%
  group_by(ParticipantID) %>%
 filter(n != 23)

# Are there the right number of trials per block?   

## Exposure (8)  
data %>%
  group_by(ParticipantID, Phase, Block, Trial) %>%
  summarise() %>% 
  filter(Block != 1) %>%
  tally() %>%
  filter(Phase == "Exposure") %>%
  filter(n != 8)

### 2 Critical Items and 6 Filler Items / Exposure Block  
data %>%
  group_by(ParticipantID, Phase, Block, Item.Type, Trial) %>%
  summarise() %>%   
  tally() %>%
  filter(Phase == "Exposure") %>%
  filter(Item.Type == "Critical" & n != 2 | 
         Item.Type == "Filler" & n != 6)

## Test Block (6)  
data %>%
  group_by(ParticipantID, Phase, Block, Trial) %>%
  summarise() %>% 
  filter(Block != 1) %>%
  tally() %>%
  filter(Phase == "Test") %>%
  filter(n != 6)

### All Test Items / Test Block  
data %>%
  group_by(ParticipantID, Phase, Block, Item.Type, Trial) %>%
  summarise() %>%   
  tally() %>%
  filter(Phase == "Test") %>%
  filter(Item.Type == "Test" & n !=  6)
```

# Exclusions    
```{r Survey Questions}
# Reported Attending to the wrong talker
data %>%
  group_by(ParticipantID, Phase, Correct_Attended.Talker) %>%
  filter(Phase == "Exposure") %>%
  filter(Correct_Attended.Talker != "TRUE") %>%
  tally()

  ## 1 participant (P.533) excluded due to incorrectly responding which talker they were attending to during the exposure phase
  data.A <- data %>%
      group_by(ParticipantID, Phase, Correct_Attended.Talker) %>%
      filter(Phase == "Exposure") %>%
      filter(Correct_Attended.Talker != "FALSE") %>%
      ungroup()

  data.A

# Reported using incorrect equipment 
data.A %>%
  group_by(ParticipantID, audio_type) %>%
  filter(audio_type != "in-ear") %>%
  filter(audio_type != "over-ear") %>%
  summarise()

## 1 participant (P. 454) excluded due to reporting they used external laptop speakers during the experiment
  data.B <- data.A %>%
    group_by(ParticipantID, audio_type) %>%
    filter(audio_type != "computer speakers") %>%
    ungroup()

  data.B
```

# Performance
## Lexcical Decision Task  
```{r Performance}
## Performance before exclusions
X <- data.B %>%
  group_by(ParticipantID, Phase, Response.Correct) %>%
  filter(Phase == "Exposure") %>%  ## Remove the practice trials
  filter(Response.Correct == "FALSE") %>%
  tally() 
X
## 59 of the remaining 62 participants answered at least 1 question incorrectly (# of rows)

# Correct Responses to the filler items and the unshifted filler items
Resp_False <- data.B %>%
  group_by(ParticipantID, Phase, Response.Correct) %>%
  filter(Phase == "Exposure") %>%  ## Remove the practice trials
  #filter(Attended.Talker_Version == "Unshifted" | Item.Type == "Filler") %>%
  filter(Response.Correct == "FALSE") %>%
  tally()
Resp_False

Resp_False_Max <- 0.20 * 80   # Number of trials can get incorrect; 80% correct (60+)
                             
Resp_False %>%
  filter(n >= Resp_False_Max)

## Remove P.461 and P.467 for # of incorrect responses 
data.C <- data.B %>%
  group_by(ParticipantID) %>% 
  filter(ParticipantID != 461) %>%
  filter(ParticipantID != 467) %>%
  ungroup()

data.C %>%
  group_by(ParticipantID, Response.Correct) %>%
  tally() ## Check number of rows; all intended participants excluded? -> should be 4


# Get avg. sd incorrect responses
C <- data.C %>%
  group_by(ParticipantID, Phase, Response.Correct) %>%
  filter(Phase == "Exposure") %>%  ## Remove the practice trials
  filter(Response.Correct == "FALSE") %>%
  tally() 

mean(C$n)
sd(C$n)
```

## Critical Shifted Items
```{r Critical ? Trials}
# Correct Responses (8) for the shifted critical items (10)
## Backed by previous lit

Crit.Resp_False <- data.C %>%
  group_by(ParticipantID, Item.Type, Attended.Talker_Version, Response.Correct) %>%
  filter(Item.Type == "Critical") %>% 
  filter(Attended.Talker_Version == "Shifted") %>%
  filter(Response.Correct == "FALSE") %>%
  tally()

Crit.Resp_False

Crit.Resp_False_Max <- 4
# 10 shifted critical Items; must recognize at least 6 of the critical shifts as words to expect adaptation.
Crit.Resp_False %>%
  filter(n > Crit.Resp_False_Max)

## Remove P.548 for too many incorrect Critical Trials
data.D <- data.C %>%
  group_by(ParticipantID) %>% 
  filter(ParticipantID != 548) %>%
  ungroup()

data.D %>%
  group_by(ParticipantID) %>%
  tally()
```

```{r Avg/sd incorrect responses}
Resp_False <- data.D %>%
  group_by(ParticipantID, Phase, Response.Correct) %>%
  filter(Phase == "Exposure") %>%  ## Remove the practice trials
  #filter(Attended.Talker_Version == "Unshifted" | Item.Type == "Filler") %>%
  filter(Attended.Talker_Version == "Shifted") %>%
  filter(Response.Correct == "FALSE") %>%
  tally() ## stats for the number of critical trials incorrect

Resp_False

  avg_Resp.False <- mean(Resp_False$n)
  avg_Resp.False              # Print Mean incorrect trials

  sd_Resp.False <- sd(Resp_False$n)
  sd_Resp.False

# (sd_Resp.False * 3) + avg_Resp.False  ## validate correct response exclusion criteria
```

# Sig. difference between Response.Correct exclusions between conditions
```{r sig diff}
## All Trial Responses
A1 <- data.C %>%  # data.C before Response.Correct exclusions
  group_by(ParticipantID, Response.Correct) %>%
  filter(Response.Correct == "FALSE") %>%
  group_by(Attended.Talker_Sound, Attended.Talker_Version) %>%
  tally() 

A2 <- data.D %>%
  group_by(ParticipantID, Response.Correct) %>%
  filter(Response.Correct == "FALSE") %>%
  group_by(Attended.Talker_Sound, Attended.Talker_Version) %>%
  tally() 

A1
A2

# Only Critical Responses, separated by sound + version
B1 <- data.C %>%  # data.C before Response.Correct exclusions
  group_by(ParticipantID, Response.Correct) %>%
  filter(Response.Correct == "FALSE") %>%
  group_by(ParticipantID, Attended.Talker_Sound, Attended.Talker_Version) %>%
  filter(Item.Type == "Critical") %>%
  group_by(Attended.Talker_Sound, Attended.Talker_Version) %>%
  tally() 

B2 <- data.D %>%  
  group_by(ParticipantID, Response.Correct) %>%
  filter(Response.Correct == "FALSE") %>%
  group_by(ParticipantID, Attended.Talker_Sound, Attended.Talker_Version) %>%
  filter(Item.Type == "Critical") %>%
  group_by(Attended.Talker_Sound, Attended.Talker_Version) %>%
  tally()

B1
B2

# Only Critical Responses, separated by Gender
C1 <- data.C %>%  # data.C before Response.Correct exclusions
  group_by(ParticipantID, Response.Correct) %>%
  filter(Response.Correct == "FALSE") %>%
  group_by(ParticipantID, Attended.Talker_Sound, Attended.Talker_Version, Attended.Talker_Gender) %>%
  filter(Item.Type == "Critical") %>%
  group_by(Attended.Talker_Gender, Attended.Talker_Sound, Attended.Talker_Version) %>%
  tally()

C2 <- data.D %>%  
  group_by(ParticipantID, Response.Correct) %>%
  filter(Response.Correct == "FALSE") %>%
  group_by(ParticipantID, Attended.Talker_Sound, Attended.Talker_Version, Attended.Talker_Gender) %>%
  filter(Item.Type == "Critical") %>%
  group_by(Attended.Talker_Gender, Attended.Talker_Sound, Attended.Talker_Version) %>%
  tally()

C1
C2

## Difference between item type (filler words/nonewords, critical s/sh shifted/unshifted)
table(A1$n, A2$n)
chisq.test(table(A2$n, A1$n))

# Difference between critical items (critical s/sh shifted/unshifted) 
table(B1$n, B2$n)
chisq.test(table(B2$n, B1$n))

# Difference between critical items by gender (F/M critical s/sh shifted/unshifted)
table(C1$n, C2$n)
chisq.test(table(C2$n, C1$n))

# No statistical sig. diff (P > .05) between how exclusion criteria applied to participants across conditions 

## Double check this is actually functioning as intended
```

# Plot data  
```{r}
data %>%
  group_by(ParticipantID) %>%
   filter(ParticipantID != 461) %>%
   filter(ParticipantID != 467) %>%
   filter(ParticipantID != 533) %>%
   filter(ParticipantID != 548) %>%
  
  
   select(-c("...1")) %>%
view()
 #write.csv(., "C:/Users/Rachel/Documents/SI.SP/data/exp.1_data.csv", row.names = FALSE)
```

```{r}
Data <- read_csv("C:/Users/Rachel/Documents/SI.SP/data/exp.1_data.csv",
    show_col_types = FALSE)
```

# Average Participant Age
```{r age}
x <- Data %>%
  group_by(ParticipantID, Participant.Age) %>%
  filter(Participant.Age != "NA") %>%
  summarize()

X
mean(x$Participant.Age)
sd(x$Participant.Age)

Data %>%
  group_by(ParticipantID,Participant.Sex ) %>%
  
```
# Comments
```{r comments}
Data %>%
  group_by(ParticipantID, Assignment.Comment) %>%
  filter(Assignment.Comment != "NA") %>%
  summarise()
```

# Survey
```{r}
Data %>%
  group_by(ParticipantID, Condition_Attended.Label, speaker_attended_ssh, speaker_unattended_ssh) %>%
  filter(speaker_unattended_ssh != "normal") %>%
  #filter(speaker_attended_ssh != "normal") %>%
  filter(Condition_Attended.Label == "?s") %>%
  summarise()
```

# Results
## Attended Talker 
```{r, Attended Talker Resp}
Data %>%                           
  
  filter(Item.Type == "Test") %>%
  mutate(Response.Ashi = ifelse(Response == "ASHI", 1, 0)) %>%
  
  # Attended Talker
  mutate(Attended.Talker_Test = ifelse(Attended.Talker_Gender == Condition_Attended.Gender, "Attended Talker", "Unattended Talker")) %>% 
  
  group_by(ParticipantID, Attended.Talker_Test,   Condition_Attended.Label, Attended.Talker_Item) %>%
  summarise(Response.Ashi = mean(Response.Ashi)) 
```

# See vars  
```{r}
Data %>%
  view()
```

##Figures  
# By attended Talker
```{r, fig.width=10, fig.height=5, warning=FALSE, fig.cap="Figure X: Compares the average proportion of ASHI responses for the Attended Talker and the Unattended Talker across ?s (blue curve) and ?sh (orange curve) shift conditions. The curves intercept the gray dashed line estimates when participants are equally likely to respond either ASI or ASHI for the test token."}

Data %>%    
  filter(Phase == "Test") %>%
  mutate(
    Response.Ashi = ifelse(Response == "ASHI", 1, 0),
    Attended.Talker_Test = ifelse(Attended.Talker_Gender == Condition_Attended.Gender, "Attended Talker", "Unattended Talker"),
    Attended.Talker_Item = 32 - as.numeric(gsub("ashi.(.*)$", "\\1", Attended.Talker_Item))) %>%  ## total cont. = 31 steps Lui & Jaeger
  
 group_by(ParticipantID, Attended.Talker_Test, Condition_Attended.Gender, Attended.Talker_Gender, Condition_Attended.Label, Attended.Talker_Item) %>%
  summarise(Response.Ashi = mean(Response.Ashi)) %>%
  
  mutate(Ambiguous_Sound = case_when(
  Attended.Talker_Test == "Attended Talker" ~ Condition_Attended.Label,
  Attended.Talker_Test != "Attended Talker" & Condition_Attended.Label == "?s" ~ "?sh",
  Attended.Talker_Test != "Attended Talker" & Condition_Attended.Label == "?sh" ~ "?s",
  T ~ NA
  )) %>%
    
  mutate(Ambiguous_Sound = gsub( "$", " sound", Condition_Attended.Label)) %>%
 
  ggplot(aes(
    x = Attended.Talker_Item, 
    y = Response.Ashi,
    color = Ambiguous_Sound,
    fill = Ambiguous_Sound
    )) +
  
  stat_summary(fun.data = mean_cl_boot, geom = "pointrange", position = position_dodge(.1)) +
 
  geom_smooth(
    method = "glm",
    formula = y ~ x, 
    method.args = list(family = "binomial"),
    show.legend = TRUE) +
  
  
  scale_color_manual(values = c("lightpink4", "lightsalmon")) +
  scale_fill_manual(values = alpha(c("lightpink4", "lightsalmon"), .1)) +
  
  # Inflection pt
  geom_segment(
    x = 7.5, xend = 32,
    y = .5, yend = .5,
    color = "darkgray", 
    linetype = 2,
    size = .75) +
 
  ## Graph aes  
  scale_x_continuous(
    name = "Test Item",  breaks = c(13, 17, 18, 19, 20, 24), labels = c("13 (Most ASI-like)", "17", "18 ", "19", "20", "24 (Most ASHI-like)"), limits = c(12, 25)) +
  scale_y_continuous("Proportion of ASHI Responses",
  limits = c(0,1)) +
facet_grid(Attended.Talker_Gender ~ Attended.Talker_Test) +
  theme(legend.position = "top")
```

# By Condition
```{r, fig.width=9.5, fig.height=4.5, warning=FALSE, fig.cap="Figure X: Compares the average proportion of ASHI responses for the Attended Talker and the Unattended Talker *within* ?s (blue curve) and ?sh (orange curve) shift conditions. The curves intercept the gray dashed line estimates when participants are equally likely to respond either ASI or ASHI for the test token."}

Data %>%    
  
  filter(Phase == "Test") %>%
  
  mutate(
    
    Response.Ashi = 
      ifelse(Response == "ASHI", 1, 0),
    
    Talker = 
      ifelse(Attended.Talker_Sound == Condition_Attended.Gender, "Attended Talker", "Unattended Talker"),
    
    Attended.Talker_Item = 
      32 - as.numeric(gsub("ashi.(.*)$", "\\1", Attended.Talker_Item)), ## 31 steps Liu & Jaeger
    
    Condition.Label = 
      gsub( "^", "Attended to ", Condition_Attended.Label)
    
    ) %>%  
  
  group_by(ParticipantID, 
          Talker, 
          Condition_Attended.Gender, 
          Attended.Talker_Gender, 
          Condition.Label, 
          Attended.Talker_Item
          ) %>%
  
  summarise(Response.Ashi = mean(Response.Ashi, )) %>%
 
  ggplot(aes(
    x = Attended.Talker_Item, 
    y = Response.Ashi,
    color = Talker,
    fill = Talker
    )) +
  
  stat_summary(
    fun.data = mean_cl_boot, geom = "pointrange", position = position_dodge(.1)
    ) +
 
  geom_smooth(
    method = "glm",
    formula = y ~ x, 
    method.args = list(family = "binomial"),
    show.legend = TRUE) +
  
  # Inflection pt
  geom_segment(
    x = 7.5, xend = 32,
    y = .5, yend = .5,
    color = "darkgray", 
    linetype = 2,
    size = .75) +
  
  ## Graph aes  
  scale_color_manual(values = c("lightskyblue", "orange")) +
  scale_fill_manual(values = alpha(c("lightskyblue", "orange"), .1)) +
  
  scale_x_continuous(
    name = "Test Item",  breaks = c(13, 17, 18, 19, 20, 24), labels = c("13 (Most ASI-like)", "17", "18 ", "19", "20", "24 (Most ASHI-like)"), limits = c(12, 25)) +
  scale_y_continuous("Proportion of ASHI Responses (%)",
  limits = c(0,1)) +
  facet_wrap( ~ Condition.Label) +
  theme(legend.position = "top")
```

## Split by gender
```{r, fig.width=4, fig.height=2, warning=FALSE, fig.cap=""}
Data %>%    
  filter(Phase == "Test") %>%
  mutate(
    Response.Ashi = ifelse(Response == "ASHI", 1, 0),
    Attended.Talker_Test = ifelse(Attended.Talker_Gender == Condition_Attended.Gender, "Attended Talker", "Unattended Talker"),
    Attended.Talker_Item = 32 - as.numeric(gsub("ashi.(.*)$", "\\1", Attended.Talker_Item))) %>%  ## total cont. = 31 steps Lui & Jaeger
  
  group_by(ParticipantID, Attended.Talker_Test, Condition_Attended.Gender, Attended.Talker_Gender, Condition_Attended.Label, Attended.Talker_Item) %>%
  summarise(Response.Ashi = mean(Response.Ashi)) %>%
 
  ggplot(aes(
    x = Attended.Talker_Item, 
    y = Response.Ashi,
    color = Condition_Attended.Label,
    fill = Condition_Attended.Label
    )) +
  
  stat_summary(fun.data = mean_cl_boot, geom = "pointrange", position = position_dodge(.1)) +
 
 geom_smooth(
    method = "glm",
    formula = y ~ x, 
    method.args = list(family = "binomial"),
    show.legend = TRUE) +
 
  scale_color_manual(values = c("lightskyblue", "orange")) +
  scale_fill_manual(values = alpha(c("lightskyblue", "orange"), .1)) + 
  
    # Inflection pt
  geom_segment(
    x = 7.5, xend = 22.5,
    y = .5, yend = .5,
    color = "darkgray", 
    linetype = 2,
    size = .75) +
 
  ## Graph aes  
  scale_x_continuous("Continuum Step (ASI -> ASHI)") +
  scale_y_continuous("Proportion of ASHI Responses (%)",
  limits = c(0,1)) +
  facet_grid(Condition_Attended.Gender ~ Attended.Talker_Test) +
  theme(legend.position = "top")
```

# Grid of test responses in order
```{r, fig.width= 11, fig.height= 7, warning=FALSE, fig.cap="Figure X: Each column represents a participant (vertically, across both panes; need to change X-axis scale; ?s has 32 participants and ?sh has 26), and each row represented the continuum step (Ashi.19 = ss, 1, Ashi.08 = sh, 0). The fill represents the participants number of Asi-Ashi response for that item."}
Data %>%
  filter(Phase == "Test") %>% 
  mutate(
    Response.Ashi = 
      ifelse(Response == "ASHI", 0, 1),
    Attended.Talker_Test = 
      ifelse(Attended.Talker_Gender == Condition_Attended.Gender, "Attended Talker", "Unattended Talker"),
    Item = Attended.Talker_Item
    ) %>%
     
  group_by(ParticipantID, Attended.Talker_Test, Attended.Talker_Gender, Condition_Attended.Label, Attended.Talker_Item) %>%
  
  mutate(Number.of_Ashi.Responses = (6 * mean(Response.Ashi))) %>%
  mutate(Condition.Label = gsub( "^", "Condition: Attended to ", Condition_Attended.Label)) %>%
  
  
  ggplot(aes(x = ParticipantID, y = Item)) +
  geom_col(aes(fill = Number.of_Ashi.Responses)) +
  
  scale_x_continuous(name = "Participant", breaks = NULL) + 
  scale_y_discrete(name = "Test Item", breaks = waiver(), labels = c("Most ASI-like: 13", "17", "18 ", "19", "20", "Most ASHI-like: 24")) +
  scale_fill_viridis_b(option = "rocket", breaks = seq(0, 6, by = (1))) +
  coord_cartesian(expand = F) +
  facet_grid(Attended.Talker_Test ~ Condition.Label, 
    scales = "free_x", 
    space = "free_x") +
  theme(legend.position = "top") +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r ANOVA}
X <- Data %>%
  filter(Phase == "Test") %>% 
  filter(Block < 17) %>%
  mutate(
    Response.Ashi = 
      ifelse(Response == "ASHI", 0, 1),
    
    Talker = 
      ifelse(Attended.Talker_Gender == Condition_Attended.Gender, "Attended Talker", "Unattended Talker"),
    
    Item = Attended.Talker_Item
  
    ) %>%
     
  group_by(ParticipantID, Talker, Attended.Talker_Gender, Condition_Attended.Label, Attended.Talker_Item) %>%
  mutate(avg.Response = mean(Response.Ashi)) %>%
  mutate(Number.of_Ashi.Responses = (6 * mean(Response.Ashi))) %>%
  mutate(Condition.Label = gsub( "^", "Condition: Attended to ", Condition_Attended.Label)) 

ggplot(X, aes(x = Item, y = avg.Response, color = Condition.Label)) + 
  geom_boxplot() +
  scale_x_discrete("Continuum Step (ASI -> ASHI)") +
  scale_y_discrete("Proportion of ASHI Responses (%)", limits = c(0,1)) +
  facet_grid( ~ Talker) +
  theme(legend.position = "top")

model = lm(avg.Response ~ Item * Talker, data = X)

lm(avg.Response ~ Item, X)

aov(avg.Response ~ Item + Condition.Label * Item + Talker, data = X)
```

# by gender and by block  
```{r, fig.width=10, fig.height=7, warning=FALSE, fig.cap="Figure X: Compares the proportion of ASHI responses across participants by block for both talkers by shift conditon and talker gender. Ribbon represents 95% confidence interval."}
Data %>%    
  filter(Phase == "Test") %>%
  mutate(
    Response.Ashi = ifelse(Response == "ASHI", 1, 0),
    Talker = ifelse(Attended.Talker_Gender == Condition_Attended.Gender, "Attended Talker", "Unattended Talker")) %>%
  
  group_by(ParticipantID, Talker, Condition_Attended.Gender, Attended.Talker_Gender, Condition_Attended.Label, Block) %>%
  summarise(Response.Ashi = mean(Response.Ashi)) %>%
   mutate(Condition.Label = gsub( "^", "Attended to ", Condition_Attended.Label)) %>%
  mutate(Attended.Gender = gsub("^", "Attended Talker Gender: ", Condition_Attended.Gender)) %>%
 
  ggplot(aes(
    x = Block, 
    y = Response.Ashi,
    color = Talker,
    fill = Talker
    )) +

  stat_summary(fun.data = mean_cl_boot, geom = "ribbon", alpha = .3, aes(group = paste(Condition_Attended.Label, Attended.Gender, Talker)))  +
  
  stat_summary(fun.y = mean, geom = "line", aes(group = paste(Condition_Attended.Label, Attended.Gender,  Talker))) +
  
  stat_summary(fun.data = mean_cl_boot, geom = "pointrange", position = position_dodge(.1)) +

  scale_color_manual(values = c("lightskyblue", "orange")) +
  scale_fill_manual(values = c("lightskyblue", "orange")) +
  
  ## Graph aes  
  ggtitle("Proportion of ASHI responses by Block for the Attended Talker and Unattended Talker, separated by Attended Talker Gender") + 
  scale_x_continuous("Block") +
  scale_y_continuous("Proportion of ASHI Responses (%)",
  limits = c(0,1)) +
  facet_grid(Attended.Gender ~ Condition.Label) +
  theme(legend.position = "top")
```


```{r, fig.width=6, fig.height=3, warning=FALSE, fig.cap="Figure X: Compares the average proportion of ASHI responses for the Attended Talker and the Unattended Talker *within* ?s (blue curve) and ?sh (orange curve) shift conditions. The curves intercept the gray dashed line estimates when participants are equally likely to respond either ASI or ASHI for the test token."}

Data %>%    
  
  filter(Phase == "Test") %>%
  filter(Block < 18) %>%
  
  mutate(
    
    Response.Ashi = 
      ifelse(Response == "ASHI", 1, 0),
    
    Talker = 
      ifelse(Attended.Talker_Gender == Condition_Attended.Gender, "Attended Talker", "Unattended Talker"),
    
    Attended.Talker_Item = 
      32 - as.numeric(gsub("ashi.(.*)$", "\\1", Attended.Talker_Item)), ## 31 steps Liu & Jaeger
    
    Condition.Label = 
      gsub( "^", "Condition: Attended to ", Condition_Attended.Label)
    
    ) %>%  
  
  group_by(ParticipantID, 
          Talker, 
          Condition_Attended.Gender, 
          Attended.Talker_Gender, 
          Condition.Label, 
          Attended.Talker_Item, 
          Block
          ) %>%
  
  summarise(Response.Ashi = mean(Response.Ashi, )) %>%
 
  ggplot(aes(
    x = Attended.Talker_Item, 
    y = Response.Ashi,
    color = Talker,
    fill = Talker
    )) +
  
  stat_summary(
    fun.data = mean_cl_boot, geom = "pointrange", position = position_dodge(.1)
    ) +
 
  geom_smooth(
    method = "glm",
    formula = y ~ x, 
    method.args = list(family = "binomial"),
    show.legend = TRUE) +
  
  # Inflection pt
  geom_segment(
    x = 7.5, xend = 32,
    y = .5, yend = .5,
    color = "darkgray", 
    linetype = 2,
    size = .75) +
  
  ## Graph aes  
  scale_color_manual(values = c("lightskyblue", "orange")) +
  scale_fill_manual(values = alpha(c("lightskyblue", "orange"), .1)) +
  
  scale_x_continuous(
    name = "ASI -> ASHI") +
  scale_y_continuous("Proportion of ASHI Responses (%)",
  limits = c(0,1)) +
  facet_wrap(~ Condition.Label + Block) +
  theme(legend.position = "top")
```



 



